---
name: Abhishek
surname: Kumar
position: "Senior Research Fellow"
address: "Department of Botany, Panjab University, Chandigarh"
profilepic: square.jpg
#phone: +91 90344 73233
email: "abhikumar.pu@gmail.com"
www: akumar.netlify.app
#orcid: 0000-0003-2252-7623
researchgate: Abhishek-Kumar-331
twitter: abkumar_
#github: abhikumar86
#linkedin: abhikumar86
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "414141"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
library(vitae)
```


# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Doctor of Philosophy (Botany)", "2017-Present", "Panjab University", "Chandigarh, India",
  "Master of Science (Botany)", "2015-2017", "Panjab University", "Chandigarh, India",
  "Bachelor of Science (Botany, Chemistry, Zoology)", "2012-2015", "Arya PG College", "Panipat, India"
) |> 
  detailed_entries(Degree, Year, Institution, Where)
```


# Selected Publications

Please check my [*website*](https://akumar.netlify.app) for a complete list of [*publications*](https://akumar.netlify.app/publication/).

## Journal articles

```{r}
bibliography_entries("mypubs.bib") |> 
    filter(type == "article-journal") |>
    arrange(desc(issued))
```

## Book chapters

```{r}
bibliography_entries("mypubs.bib") |> 
    filter(type == "chapter") |>
    arrange(desc(issued))
```


# Awards and Distinctions

```{r dist}
# what, when, with, where, why
tribble(
  ~what, ~date, ~org, 
  "Young Scientist Award", "2022", "Punjab Academy of Sciences, Patiala",
  "Best Poster Award", "2020", "National Conference on Climate Change, CSIR-NBRI, Lucknow",
  "Junior Research Fellowship", "2017", "University Grants Commission, New Delhi") |> 
    detailed_entries(what = org, when = date, with = what, .protect = F)
```

# Research Interests

- **Macroecology** Elevational patterns of plant species richness; Climate associated plant redistributions

- **Community Ecology** Diversity and distribution of plant communities along elevation and their controlling factors

- **Population Ecology** Population dynamics of mountain trees (*Pinus*, *Quercus* and *Rhododendron*); species distribution modelling

- **Ecophysiology** Variation of functional traits with environmental variables (elevation, temperature, rainfall and atmospheric pressure)

- **Ecosystem Ecology** Nutrient cycling in tropical forests; role of phosphorus and mycorrhizal fungi in litter decomposition

- **Restoration Ecology** Ecological restoration of coal mine spoils

# Skills and Qualifications

Please check my [*website*](https://akumar.netlify.app) for a comprehensive list of [*accomplishments*](https://akumar.netlify.app/accomplishment/) and certificates

- `R`
- Microsoft Office (Excel, PowerPoint, Word)
- Biostatistics
- Data analysis and visualisation
- Systematic reviews and meta-analysis
- Scientific and technical writing

# Professional Memberships

- Student Member (#67527876), [*International Association for Vegetation Science*](https://iavs.org)
- Life Member (#L-1599), *Punjab Academy of Sciences, Patiala*


# References

- **Dr. Anand Narain Singh**, Panjab University, Chandigarh, dranand1212@gmail.com
- **Prof. Amrik Singh Ahluwalia**, Eternal University, Sirmaur, amrik.s511@gmail.com
- **Dr. Balkar Singh**, Arya PG College, Panipat, balkararya@gmail.com


